Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-20 doc/Paper/main.tex
Switched from Omega_c to Omega_m and fixed bias plot.

    To illustrate the cosmological constraining power of the data considered in our analysis, we allow for variations in the r.m.s. of linear matter fluctuations in spheres of comoving radius 8 $h^{-1}$ Mpc, $\sigma_{8}$, and the fractional cold matter density today, $\Omega_{c}$, in addition to our baseline set of parameters (c.f. Sec.~\ref{ssec:methods.constr}). All other cosmological parameters remain fixed to their fiducial Planck 2018 values. From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{m} = 0.298 \pm 0.025$,
%%%-> 0.247+0.0493+0.06/93.4/0.7**2 = 0.297611
    consistent with our assumed fiducial cosmology.  In particular, this is consistent with Planck and BAO measurement, which give $\Omega_m=0.3110\pm 0.006$ and $\sigma_8=0.8099 \pm 0.0071$ \cite{1807.06209} albeit with a different parameterization. The HSC analysis of the weak lensing data from the the full first year HSC data (similar in size, but somewhat larger than the public release) gives $\Omega_m=0.346^{+0.052}_{-0.100}$ \cite{1906.06041}, showing an excellent internal consistency. We note that our modeling makes considerably stronger modeling assumption and thus gives errorbars that are likely under-estimated.

@@

    \begin{figure}
      \begin{center}
        \includegraphics[width=0.49\textwidth]{figures/contours-Oc-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.). \as{Can we replot this as $\Omega_m$ rather than $\Omega_c$.?}}
        \label{fig:constraints-fit=Oc+s8}
      \end{center}
    \end{figure}

@@

This analysis yields a few interesting results. First we find that the approximation $b(z)\propto D(z)^{-1}$ (i.e $\alpha=-1$ is only approximately valid. In fact, there is no physical reason for it, because the cut is on the observed magnitude, so at the same observed magnituce cut, the low redshift galaxies are \emph{different population} of galaxies. We find that the bias increases somewhat faster than the standard empirical assumption of $D(z)^{-1}$.

@@

An alternative use is galaxy evolution studies, where this results provides a convenient cross-check formula. Our full parameter chains for different magnitudes are available upon request. \as{Is this the case?}

>>>>

    To illustrate the cosmological constraining power of the data considered in our analysis, we allow for variations in the r.m.s. of linear matter fluctuations in spheres of comoving radius 8 $h^{-1}$ Mpc, $\sigma_{8}$, and the fractional cold matter density today, $\Omega_{c}$, in addition to our baseline set of parameters (c.f. Sec.~\ref{ssec:methods.constr}). All other cosmological parameters remain fixed to their fiducial Planck 2018 values. From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{m} = 0.286 \pm 0.025$,
%%%-> 0.247+0.0493+0.06/93.4/0.7**2 = 0.297611
    consistent with our assumed fiducial cosmology.  In particular, this is consistent with Planck and BAO measurement, which give $\Omega_m=0.3110\pm 0.006$ and $\sigma_8=0.8099 \pm 0.0071$ \cite{Planck:2018} albeit with a different parameterization. The HSC analysis of the weak lensing data from the the full first year HSC data (similar in size, but somewhat larger than the public release) gives $\Omega_m=0.346^{+0.052}_{-0.100}$ \cite{1906.06041}, showing an excellent internal consistency. We note that our analysis makes considerably stronger modeling assumption and thus gives errorbars that are likely under-estimated.

@@

    \begin{figure}
      \begin{center}
        \includegraphics[width=0.49\textwidth]{figures/contours-Om-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
        \label{fig:constraints-fit=Oc+s8}
      \end{center}
    \end{figure}

@@

This analysis yields a few interesting results. First we find that the approximation $b(z)\propto D(z)^{-1}$ (i.e $\alpha=-1$ is only approximately valid. In fact, there is no physical reason for it, because the cut is on the observed magnitude, so at the same observed magnitude cut, the low redshift galaxies are \emph{different population} of galaxies. We find that the bias increases somewhat faster than the standard empirical assumption of $D(z)^{-1}$.

@@

An alternative use is galaxy evolution studies, where this results provides a convenient cross-check formula. Our full parameter chains for different magnitudes are available upon request. \as{Is this the case?} \an{That would be totally fine with me.}
